\documentclass[11pt, a4paper, DIV=12]{scrartcl}

\usepackage[english]{babel}
\usepackage{cmap}       
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{exscale}
\usepackage[l2tabu, orthodox]{nag}
\usepackage[symbol]{footmisc}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}


\setlength\parindent{0in} 
\usepackage[usenames,dvipsnames]{xcolor} 
\definecolor{maroon}{rgb}{0.5, 0.0, 0.0}
\definecolor{upmaroon}{RGB}{133, 75, 91}
\definecolor{upgrey}{RGB}{99, 124, 128}

\definecolor{upblack}{RGB}{64, 62, 48}
\definecolor{upbeige}{RGB}{224, 229, 224}


\usepackage[
bookmarks, 
colorlinks, 
breaklinks, 
pdftitle={Noman Bashir -- CV},
pdfauthor={Noman Bashir}
]{hyperref}
\hypersetup{linkcolor=black,citecolor=blue,filecolor=black,urlcolor=black}

\usepackage{url}

\usepackage{microtype}
\usepackage{ellipsis}
\usepackage{xspace}
\usepackage{hfoldsty}

\usepackage{ifthen}
\newcommand{\CC}[1][]{$\text{C\hspace{-.25ex}}^{_{_{_{++}}}}
	\ifthenelse{\equal{#1}{}}{}{\text{\hspace{-.625ex}#1}}$}

%\addtokomafont{disposition}{\rmfamily}
%\addtokomafont{descriptionlabel}{\rmfamily}
%\usepackage{lmodern}
\usepackage[varqu]{zi4}
%\usepackage[sfdefault]{classico}
\usepackage[tt=false]{libertine}
%\usepackage[]{classico}
\usepackage[varqu]{zi4}
\usepackage[libertine]{newtxmath}
%\usepackage[]{helvet}

\begin{document}

\section*{\textcolor{upmaroon}{Curriculum vitæ}}
\vspace{-20pt}
\hrulefill
\subsection*{Address}
\noindent
\begin{tabular}{l}
Noman Bashir\\
University of Massachusetts Amherst\\ 
206 Knowles Engineering Building\\ 
Amherst, MA, 01002\\
E-mail: \texttt{nbashir@umass.edu} \\
Homepage: \url{https://noman-bashir.github.io/}\\
\end{tabular}

\subsection*{Areas of Specialization}
\noindent
\begin{tabular}{p{15.0cm}}
Designing sustainable, equitable, and explainable computing systems, e.g., edge, cloud, datacenters, and cyber-physical systems, e.g., electric grid.
\end{tabular}

\subsection*{Education}
\noindent
\begin{tabular}{p{3.0cm}p{11.5cm}}
	08/2016--02/2022&PhD in Computer Engineering, University of Massachusetts Amherst\\
	09/2013--03/2016&MS Energy Systems Engineering, National University of Science and Technology, Islamabad, Pakistan\\
	09/2009--05/2013&BS Electrical Engineering, University of Engineering and Technology, Lahore, Pakistan\\
\end{tabular}

\subsection*{Employment}
\begin{tabular}{p{3.0cm}p{11.5cm}}
	09/2016--present&PhD student and graduate research assistant, Sustainable Computing Lab, University of Massachusetts Amherst, advised by David Irwin.\\
	05/2021--08/2021& Student researcher at VMware Research Group. Hosted by Ben Pfaff and Victor Firoiu.\\
	05/2020--11/2020& Student researcher at the SysInfra/Borg team inside Google. Hosted by Nan Deng and Krzysztof Rzadca.\\
	05/2015--06/2016&Research associate, Advanced Communication Lab, Lahore University of Management Sciences (LUMS), advised by Naveed-ul-Hassan.\\
	09/2013--05/2015&Research engineer, Systems and Networks (SysNet) Lab, National University of Computer and Emerging Sciences, Pakistan, advised by Affan A. Syed.\\
\end{tabular}

\renewcommand{\refname}{\large\bfseries Publications}



\begin{thebibliography}{5}

\subsubsection*{Conference Papers}

	\bibitem{Mor+2015}
	Noman Bashir, Tian Guo, Mohammad Hajiesmaili, David Irwin, Prashant Shenoy, Ramesh Sitaraman, Abel Souza, Adam Wierman.
	\emph{Enabling Sustainable Clouds: The Case for Virtualizing the Energy System}, 
	 ACM Symposium on Cloud Computing (SoCC), 2021. 
	


	\bibitem{Mor+2015}
    Pradeep Ambati, Noman Bashir, David Irwin, Prashant Shenoy.
	\emph{Good Things Come to Those Who Wait: Optimizing Job Waiting in the Cloud},
	ACM Symposium on Cloud Computing (SoCC), 2021.	

	\bibitem{Mor+2015}
	Noman Bashir, Nan Deng, Krzysztof Rzadca, David Irwin, Sree Kodak, Rohit Jnagal.
	\emph{Take it to the Limit: Prediction-Driven Resource Overcommitment in Datacenters},
    European Conference on Computer Systems (EuroSys), 2021, Artifact Badges: Available, Functional, and Results Reproduced.	

	\bibitem{Mor+2015}
	Noman Bashir, David Irwin, Prashant Shenoy.
	\emph{DeepSnow: Modeling the Impact of Snow on Solar Generation},
	ACM International Conference on Systems for Energy-Efficient Buildings, Cities, and Transportation (BuildSys), 2020.

	\bibitem{Mor+2020}
    Noman Bashir, David Irwin, Prashant Shenoy.
	\emph{A Probabilistic Approach to Committing Solar Energy in Day-ahead Electricity Markets},
	International Green and Sustainable Computing Conference (IGSC), 2020.

	\bibitem{Fey+2020}
	Pradeep Ambati, Noman Bashir, David Irwin, Prashant Shenoy.
    \emph{Waiting Game: Optimally Provisioning Fixed Resources for Cloud-enabled Schedulers},
	Supercomputing (SC) 2020, Best Paper Award Finalist and Best Student Paper Award Finalist.
	
	\bibitem{Oet+2020}
	Santiago Correa, Noman Bashir, Andrew Tran, David Irwin, Jay Taneja.
	\emph{Extend: A Framework for Increasing Energy Access by Interconnecting Solar Home Systems},
	ACM SIGCAS Conference on Computing and Sustainable Societies (COMPASS), 2020.
	
	\bibitem{Mor+2019}
	Menghong Feng, Noman Bashir, Prashant Shenoy, David Irwin, Dragoljub Kosanovic.
	\newblock \emph{SunDown: Model-driven Per-Panel Solar Anomaly Detection for Residential Arrays},
	\newblock ACM SIGCAS Conference on Computing and Sustainable Societies (COMPASS), 2020.
	
	\bibitem{Yin+2018}
	Pradeep Ambati, Noman Bashir, Mohammad Hajiesmaili, David Irwin, Prashant Shenoy.
	\emph{Hedge Your Bets: Optimizing Long-term Cloud Costs by Mixing VM Purchasing Options},
	IEEE International Conference on Cloud Engineering (IC2E), 2020.
	
	\bibitem{Kri+2018}
	Noman Bashir, Dong Chen, David Irwin, Prashant Shenoy.
	\emph{Solar-TK: A Data-driven Toolkit for Solar PV Performance Modeling and Forecasting},
	IEEE International Conference on Mobile Ad-Hoc and Smart Systems (MASS), 2019.
	
	\bibitem{Mor+2017}
    Santiago Correa, Noman Bashir, Jesus Omana Iglesias, Candace Saffery, Jay Taneja.
	\emph{Like a Good Neighbor, Solar is There},
	The International Conference on Future Energy Systems (e-Energy), 2019.
	
	\bibitem{Mor+2017}
	Noman Bashir, David Irwin, Prashant Shenoy.
	\emph{Helios: A Programmable Software-defined Solar Module},
	ACM International Conference on Systems for Energy-Efficient Buildings, Cities, and Transportation (BuildSys), 2018.
	
	\bibitem{Mor+2016}
    Noman Bashir, David Irwin, Prashant Shenoy, Jay Taneja.
	\emph{Enforcing Fair Grid Energy Access for Controllable Distributed Solar Capacity},
	ACM International Conference on Systems for Energy-Efficient Buildings, Cities, and Transportation (BuildSys), 2017.
	
	\bibitem{Mor+2016}
    Noman Bashir, Hira Shahzad Sardar, Mashood Nasir, Naveed Ul Hassan, Hassan A. Khan.
	\emph{Lifetime Maximization of Lead-acid Batteries in Small Scale UPS and Distributed Generation Systems},
	IEEE PowerTech, 2017.

	\bibitem{Mor+2016}
    Aneeq Ur Rehman, Noman Bashir, Naveed Ul Hassan, Chau Yuen.
	\emph{Impact of Home Appliances on the Performance of Narrow-band Power Line Communications for Smart Grid Applications},
	IEEE Region Ten International Conference (TenCon), 2016.
	
	\bibitem{Mor+2016}
    Noman Bashir, Zohaib Sharani, Khushboo Qayyum, and Affan A. Syed.
	\emph{Delivering Smart Load-shedding for Highly-stressed Grids},
	IEEE International Conference on Communications, Control, and Computing Technologies for Smart Grids (SmartGridComm), 2015.


\subsubsection*{Journal Articles}

\bibitem{Mor+2020}
Pradeep Ambati, Noman Bashir, David Irwin, Prashant Shenoy.
\emph{Modeling and Analyzing Waiting Policies for Cloud-Enabled Schedulers},
IEEE Transactions on Parallel and Distributed Systems (TPDS), 2021.

\bibitem{Mor+2020}
Menghong Feng, Noman Bashir, Prashant Shenoy, David Irwin, Dragoljub Kosanovic.
\emph{Model-driven Per-Panel Solar Anomaly Detection for Residential Arrays},
ACM Transactions on Cyber-Physical Systems (TCPS), 2021.

\bibitem{Mor+2020}
Noman Bashir, David Irwin, Prashant Shenoy, Jay Taneja.
\emph{Mechanisms and Policies for Controlling Distributed Solar Capacity},
The ACM Transactions on Sensor Networks (TOSN), 2018.

\subsubsection*{Book Chapters}

\bibitem{Mor+2015}
Noman Bashir, Naveed Ul Hassan, Chau Yuen, Wayes Tushar.
\emph{Smart-grid Communications and Standard},
in \emph{IET Communication, Control and Security Challenges for the Smart Grid}, 2017.


\subsubsection*{Posters/Demos (Peer-reviewed)}

\bibitem{Mor+2020}
Santiago Correa, Noman Bashir, Jesus Omana Iglesias, Candace Saffery, Jay Taneja.
\emph{EXTEND: A Framework for Increasing Energy Access in Communities with Solar Home Systems},
ACM SIGCAS Conference on Computing and Sustainable Societies (COMPASS), 2019.

\bibitem{Mor+2020}
Noman Bashir, Dong Chen, David Irwin, Prashant Shenoy.
\emph{Solar-TK: Solar Performance Modeling and Forecasting Toolkit},
ACM International Conference on Systems for Energy-Efficient Buildings, Cities, and Transportation (BuildSys), 2019.

\bibitem{Yin+2018}
Zohaib Sharani, Noman Bashir, Khushboo Qayyum, and Affan A. Syed.
\emph{Enabling Practical Demand Response in Highly-Stressed Grids using Aashiyana},
The International Conference on Future Energy Systems (e-Energy), 2015.

\bibitem{Yin+2018}
Zohaib Sharani, Khushboo Qayyum, Noman Bashir, and Affan A. Syed.
\emph{SoftUPS: Eliminating the Need and Cost of Battery Backups},
The International Conference on Future Energy Systems (e-Energy), 2014.

\subsubsection*{Thesis}

\bibitem{Mor+2019}
Noman Bashir.
\emph{Improving the Programmability of Networked Energy Systems}, PhD thesis, University of Massachusetts Amherst, 2022.

\bibitem{Mor+2015}
Noman Bashir.
\emph{Using Stressed Grids as a Storage Medium for Renewable Energy}, MSc thesis, National University of Science and Technology (NUST), Islamabad, 2016.


	
\subsubsection*{Submitted Papers}

\bibitem{Mor+2015}
Abel Souza, Noman Bashir, Jorge Murillo, Walid Hanafy, Qianlin Liang, David Irwin, Prashant Shenoy.
\emph{Ecovisor: A Virtual Energy System for Carbon-Efficient Applications}.
	
\end{thebibliography}

\subsection*{Academic Honors}
\begin{tabular}{p{2.1cm}p{12.0cm}}
	2020& Best student paper and best paper finalist at ACM/IEEE Supercomputing (SC).\\
	2017& Best paper nomination at ACM BuildSys.\\
\end{tabular}

\subsection*{Invited Talks}
\begin{tabular}{p{2.1cm}p{12.0cm}}
04/2021& Information Technology University (ITU), Pakistan, (virtual), \emph{Leveraging Machine Learning to Design Energy Efficient and Sustainable Systems.}\\
11/2020&Energy Data Analytics Symposium, Duke University, \emph{Solar-TK: A Data-driven Toolkit for Solar PV Performance Modeling and Forecasting.}\\
\end{tabular}


% \subsection*{Teaching}
% \begin{tabular}{l}
% Supervised eight bachelor and master thesis, one intern. \\[0.5em]
% \end{tabular}

% \begin{tabular}{p{2.1cm}p{12.0cm}}
% 11/2021 & Guest lecture \emph{Introduction to Graph Neural Networks} in the \emph{Applied Machine Learning} class, McGill University\\	
	
% SS 2019&Proseminar \emph{Graph Algorithms} (supervised students and helped with organization)\\
% SS 2018&Seminar \emph{Algorithm Engineering} (supervised students and helped with organization)\\
% SS 2017&Seminar \emph{Algorithm Engineering} (supervised students and helped with organization)\\
% WS 2016/17&Student project group \emph{Algorithm Engineering for Graph Data Mining} (co-organizer), Seminar \emph{Algorithms Unplugged} (supervised students and helped with organization)\\
% SS 2016& Seminar \emph{Algorithm Engineering}, Seminar \emph{Graph Mining} (supervised students and helped with organization)\\
% As a student&Programming tutorials for engineering students, teaching assistant for a course on theoretical computer science\\
% \end{tabular}

\subsection*{Service to the Profession}

\begin{tabular}{p{14.5cm}}
Shadow PC member for ACM EuroSys 2022. \\[0.5em]
\end{tabular}

\begin{tabular}{p{14.5cm}}
Reviewer for IEEE Transactions on Parallel and Distributed Systems (TPDS) and Elsevier Sustainable
Computing (SUSCOM) journal.\\[0.5em]
\end{tabular}


% \subsection*{Grants}
% \begin{tabular}{p{14.5cm}}
% 	DFG Emmy Noether grant (own funding 1\,500\,000\,€)\\[0.5em]

% 	DAAD IFI postdoc scholarship for a 13 month stay at the Mila--Quebec AI Institute (own funding 38\,909\,€)\\[0.5em]
		
% 	Research associate and PhD student  within the Collaborative Research Center SFB 876, assisted in preparing the  grant proposal for project A6 \emph{Resource-efficient Graph Mining}
% \end{tabular}


% \subsection*{Other}

% \begin{tabular}{l}
% 	\textsf{\textbf{\em Computational Skills}} Python, C\hspace{-1pt}+\hspace{-1pt}+, \LaTeX, NumPy, Scikit-learn, PyTorch, PyTorch Geometric\\
% 	\textsf{\textbf{\em Languages}} German (native), English (fluent)\\
% 	\textsf{\textbf{\em Citizenship}} German and British
% \end{tabular}





\subsection*{References}

Furnished upon request.




\vfill{} 
\begin{center}
{\scriptsize Last updated: \today}
\end{center}



\end{document}
